---
title: "My Awesome Report"
author: "Research Student"
format: html
---

## Introduction

This report uses **tidyverse** package along with the *SAFI* data, which has columns that include:

- village
  + Name village
- interview_data
  + Date of interview
- no_members
  + How many family members live in a house?
- years_liv
  + How many years respondent has lived in village
- respondent_wall_type
  + Type of wall of house
- rooms
  + Number of rooms in house

Or, numerically:

1. village
2. interview_data
3. no_members

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(here)

interviews <- read_csv(here("data/SAFI_clean.csv"), na = "NULL"
)
```
## Tables

```{r}
#| label: tbl-interviews
#| tbl-cap: "A useful description about the table."

interviews %>%
  filter (!is.na(memb_assoc)) %>%
  group_by(village, memb_assoc) %>%
  summarize(mean_no_members = mean(no_membrs)) %>%
  knitr::kable(col.names = c("Village", "Member Association", "Mean Number of Members"))
```

## Plots!
```{r}
#| label: fig-chunk-name
#| fig-cap: "I made this amazing plot."
#| echo: false

interviews_plotting <- read_csv(here("data_output/interviews_plotting.csv"))

interviews_plotting %>%
  ggplot(aes(x = respondent_wall_tyle)) +
  geom_bar(aes(fill = village))
```
